Computing volume via non-linear rectangular prisms

### 2019-08-01 Cav2D/article-template.tex
added more text on cavalieri

\noindent
The Cavalieri integral is, however, hard to evaluate directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann integral:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx, 
\end{equation}
with $a(0) = a$, $b(0)=b$ and $h = g^{-1}$. Furthermore, $g(x) = x - a\circ f(x) + a$.

@@

\noindent
Expressing \eqref{eq:caval1} in vector calculus notation

\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx =\cint_a^b f(x)~dx, 
\end{equation}
with $\mathbf{c}(t) = <c_x(t),c_y(t)>$ denoting a vector equation that passes through the origin and is a translation of $a(y)$. We can express $a(y)$ as $\mathbf{c}(t) + <a,0>$.
Note that partition $x_i^1$ and $x_i^2$ are related to each other via: 
\begin{equation}
\label{eq:pat_rel}
<x_i^2,f(x_i^2)> = <x_i^1,0> + <c_x(t),c_y(t)> 
\end{equation}

It follows from Eq.~\eqref{eq:pat_rel} that 
\begin{equation}
c_y(t) = f(x_i^1 + c_x(t)). 
\end{equation}
We can therefore express $t$ as a function of $x_i^1$. We can now compute $h(x_i^1) = x_i^1 + t(x_i^1)$.

>>>>

\noindent
The Cavalieri integral is, however, hard to evaluate directly. Fortunately, it is easy to convert a Cavalieri integral into an equivalent Riemann integral:
\begin{equation}
\int_{a(y)}^{b(y)}f(x)\, dx = \int_{a}^{b} f\circ h(x)~dx, 
\end{equation}
with $a(0) = a$ and $b(0)=b$. The function $h$ is known as the transformation function and it maps $x_i^1\in[a,b]$ to $x_i^2\in[a',b']$. It can be constructed via the function $g(x) = x - a\circ f(x) + a$ as 
$h=g^{-1}$.

@@

\noindent
Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation. As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ?? into $\mathbb{R}^3$ is problematic. However,
if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.

\noindent
Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
\label{eq:pat_rel}
\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
\end{equation}
We can rewrite Equation~\eqref{eq:pat_rel} as
\begin{equation}
\label{eq:t_func}
c_y(t) = f(x_i^1 + c_x(t)),
\end{equation}
which highlights the fact that $t$ is a function of $x_i^1$. If we substitute $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
\begin{equation}
\label{eq:h_func}
x_i^2 = x_i^1 + c_x\circ t(x_i^1).
\end{equation}
Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
Equation~\eqref{eq:h_func} implies

% and as such $t(x_i^1)$ can be used to determine $h(x_i^1)$.
% i.e. $t$ is a function 
% It is therefore possible to define $t$ in terms of $x_i^1$.  
% \noindent
% Expressing \eqref{eq:caval1} in vector calculus notation
% \begin{equation}
% \int_{a(y)}^{b(y)}f(x)\, dx =\cint_a^b f(x)~dx, 
% \end{equation}
% with $\mathbf{c}(t) = <c_x(t),c_y(t)>$ denoting a vector equation that passes through the origin and is a translation of $a(y)$. We can express $a(y)$ as $\mathbf{c}(t) + <a,0>$.
% Note that partition $x_i^1$ and $x_i^2$ are related to each other via: 
% \begin{equation}
% \label{eq:pat_rel}
% <x_i^2,f(x_i^2)> = <x_i^1,0> + <c_x(t),c_y(t)> 
% \end{equation}
% It follows from Eq.~\eqref{eq:pat_rel} that 
% \begin{equation}
% c_y(t) = f(x_i^1 + c_x(t)). 
% \end{equation}
% We can therefore express $t$ as a function of $x_i^1$. We can now compute $h(x_i^1) = x_i^1 + t(x_i^1)$.
